Hierarchical Dispatching and Overriding

### 2017-10-03 NewVersion/sections/Formalization.tex

Finally, \textsc{(T-Intf)} defines interface checking. The
condition\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} helps to ensure unambiguity and type soundness of the calculus. We will
introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
in any case. The interface check is responsible for capturing ambiguity during compilation.

\bruno{Explanation for T-Anno is missing}

@@

\begin{figure*}[t]
\saveSpaceFig
\begin{mathpar}
	\sinvk \\
	\spathinvk \\
	% \ssuperinvk \\
	% \sstaticinvk \\
	\creceiver \hspace{.5in}
	\cpathreceiver \\
	\cargs \\
	\cpathargs \\
	% \csuperargs \\
	% \cstaticargs \\
	\cstatictype \\
	\cfreduce \\
	\cannoreduce
\end{mathpar}
\caption{Small-step semantics.}\label{fig:smallstep}
\saveSpaceFig
\end{figure*}

>>>>

Rule \textsc{(T-Intf)} defines the typing rule for interfaces. The
condition\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} helps to ensure unambiguity and type soundness of the calculus. We will
introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
in any case. The interface check is responsible for capturing ambiguity during compilation.

\bruno{Explanation for T-Anno is missing}
Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation. The rule says that $\angl{J}e$ type checks to $J$ if the expression $e$ type checks to $I$ and $I \subtype J$.

@@

\begin{figure*}[t]
\saveSpaceFig
\begin{mathpar}
	\sinvk \\
	\spathinvk \\
	% \ssuperinvk \\
	% \sstaticinvk \\
	\creceiver \hspace{.5in}
	\cpathreceiver \\
	%\cargs \\
	\cpathargs \\
	% \csuperargs \\
	% \cstaticargs \\
	\cstatictype \\
	\cfreduce \\
	\cannoreduce
\end{mathpar}
\caption{Small-step semantics.}\label{fig:smallstep}
\saveSpaceFig
\end{figure*}
